Embedding Dimension of Polyhedral Losses

### 2020-01-23 colt-20/poly-embed.tex
Added notation and definitions for embeddings, a crack at an abstract, and added .bib files

@@

% Three or more authors with the same address:
% \coltauthor{\Name{Author Name1} \Email{an1@sample.com}\\
%  \Name{Author Name2} \Email{an2@sample.com}\\
%  \Name{Author Name3} \Email{an3@sample.com}\\
%  \addr Address}

% Authors with different addresses:
\coltauthor{%
 \Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
 \addr CU Boulder
 \AND
 \Name{Rafael Frongillo} \Email{Raf@colorado.edu}\\
 \addr CU Boulder
 \AND
 \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
 \addr CU Boulder%
}

@@

\begin{abstract}%
  We far away from this.%
\end{abstract}

@@

\section{Property elicitation tools}

@@

\section{1d-characterization}

@@

% Acknowledgments---Will not appear in anonymized version
\acks{We thank a bunch of people.}

\bibliography{refs}

@@

\section{My Proof of Theorem 1}

This is a boring technical proof.

\section{My Proof of Theorem 2}

This is a complete version of a proof sketched in the main text.

>>>>

\newcommand{\hinge}{L_{\mathrm{hinge}}}
\newcommand{\ellzo}{\ell_{\text{0-1}}}
\newcommand{\ellabs}[1]{\ell_{#1}}

@@

% Three or more authors with the same address:
 \coltauthor{\Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
  \Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
  \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
  \addr CU Boulder}

% Authors with different addresses:
%\coltauthor{%
% \Name{Jessie Finocchiaro} \Email{jefi8453@colorado.edu}\\
% \addr CU Boulder
% \AND
% \Name{Rafael Frongillo} \Email{Raf@colorado.edu}\\
% \addr CU Boulder
% \AND
% \Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
% \addr CU Boulder%
%}

@@

\begin{abstract}%
  Recent work has proposed the notion of designing calibrated surrogate losses for classification-like problems through the lens of \emph{embedding} the original problem into $\reals^d$ and optimizing a polyhedral loss that is calibrated with respect to the original loss.
  In this work, we study the notion of \emph{embedding dimension} for given discrete losses.
  We characterize when a given discrete loss can be embedded into the real line, as well as when a higher-dimension input to the surrogate loss is required.
  Moreover, we give a quadratic feasibility program that yields lower bounds on the embedding dimension of a given discrete loss.
\end{abstract}

@@

\subsection{Discrete losses and embeddings}

\jessie{A lot fo this is taken from the NeurIPS paper}
Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals_+^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.

As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.

We denote surrogate losses $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$ since we are in the finite outcome setting.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.

@@

\section{1d-characterization}
\label{sec:1d}

@@

% Acknowledgments---Will not appear in anonymized version
\acks{JF- Need that GRFP acknowledgement}

\bibliography{diss,extra}

@@

\section{Additional proofs}
